Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-04-19 paper.tex
Worked on section 2.5 with @ali4006

Cycles may be present in the process graph in case a file was written
by more than one process.  We remove the cycles in the process graph
by removing file edges between processes A and B when A's process
creation timestamp is posterior to B's or when A=B \todo{to be done}.

\paragraph{} In the next step, we classify the processes into three categories based on the process graph
and the error matrix file mentioned in the previous Section:
\begin{enumerate}
\item Processes that read files that do not have errors and write files that do not have errors are \emph{transparent}.
\item Processes that read files that do not have any error but write files that have errors \emph{create} errors in the pipeline. 
\item Processes that read files that have errors and write files that do not have errors \emph{remove} errors from the pipeline.
\end{enumerate}

The classification of processes that read or write temporary files is
uncertain when these files are deleted during the execution. In such
situations, our classification marks processes as uncertain as we were
unable to find a technical solution to prevent temporary files from
being deleted by the pipeline \todo{investigate that a bit more}.

Another challenge is to classify processes that read files that have
errors and write files that also have errors. In such situations, it
is not possible to determine from the pipeline results whether
the process created errors, removed some errors, or was
transparent. We label such processes \emph{unknown}. To address this issue, we developed an iterative approach that consists of the following steps:
\begin{enumerate}
  \item Run the pipeline in conditions 1 and 2; classify the
    processes as \emph{transparent}, \emph{create errors},
    \emph{remove errors} or \emph{unknown}.
  \item If there are \emph{unknown} processes then: replace each process P that create errors by a process Q that
    copies the results produced by process P in condition 1 to the pipeline output in condition 2.
  \item Repeat steps 1 and 2 until there is no \emph{unknown} process left.
\end{enumerate}
The replacement of process P at step 2 is done by overwriting P's
executable with a custom script produced by step 1. This custom script
copies the results obtained in condition 1 if it is invoked with the
arguments of a process that created errors, and calls P's original
executable otherwise. This algorithm converges to a process graph
without any \emph{unknown} process after a finite number of iterations.

@@

>>>>

Cycles may be present in the process graph in case a file was written 
by more than one process. We remove such cycles by removing file edges 
between processes A and B when A's process creation timestamp is 
posterior to B's or when A=B. Indeed, such edges cannot happen in 
practice unless A and B were running concurrently, which we assume is 
not the case (we also checked that on the workflow we tested).

\paragraph{} In the next step, we classify the processes into three 
categories based on the process graph and the error matrix file 
mentioned in the previous Section:
\begin{enumerate}
\item Processes 
that read files that do not have errors and write files that do not 
have errors are \emph{transparent}.
\item Processes that read files 
that do not have any error but write files that have errors 
\emph{create} errors in the pipeline.
\item Processes that read files 
that have errors and write files that do not have errors\emph{remove} 
errors from the pipeline.
\end{enumerate}

The classification of processes that read or write temporary files is 
uncertain when these files are deleted during the execution. To address 
this issue, we replace every process P that writes temporary files with 
a modification of P that first calls P and then backs up all its output 
files to a read-only directory. This replacement is done by modifying 
the Unix PATH variable to point to a directory containing the modified
versions of the processes. This solution does not cover the temporary files
that are removed by P itself; this is not a problem since these files do not
play any role in the subsequent steps of the pipeline, by definition.

Files written by multiple processes also lead to unknown classification 
labels. To address this issue for a file F written by processes in 
\textbf{P} = \{$P_{1}$, \ldots $P_{n}$\}, we (1) check that processes 
in \textbf{P} do not write concurrently to F, (2) we establish an order 
on \textbf{P} based on the creation timestamp of the processes, (3) we 
replace ever process $P_{i}$ in \textbf{P} by a wrapper that first 
calls $P_{i}$ and then backs up F to a read-only directory. Thus, 
multiple versions of F are saved and used in the analysis.

Another challenge is to classify processes that read files that have
errors and write files that also have errors. In such situations, it
is not possible to determine from the pipeline results whether
the process created errors, removed some errors, or was
transparent. We label such processes \emph{unknown}. To address this issue, we developed an iterative approach that consists of the following steps:
\begin{enumerate}
  \item Run the pipeline in conditions 1 and 2; classify the
    processes as \emph{transparent}, \emph{create errors},
    \emph{remove errors} or \emph{unknown}.
  \item If there are \emph{unknown} processes then: replace each process P that create errors by a process Q that
    copies the results produced by process P in condition 1 to the pipeline output in condition 2.
  \item Repeat steps 1 and 2 until there is no \emph{unknown} process left.
\end{enumerate}
The replacement of process P at step 2 is done by replacing P
with a custom script produced by step 1. This custom script
copies the results obtained in condition 1 if it is invoked with the
arguments of a process that created errors, and calls P's original
executable otherwise. The replacement is done through the PATH variable, as before. This algorithm converges to a process graph
without any \emph{unknown} process after a finite number of iterations.

@@

\todo{Explain how graphs are represented.}
